Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-08-24 Thesis/chapter/03-theoretical-background.tex
DOE und PSO

But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
%Now, we can't - it's hard to - imagine to live without electricity. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
in chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
financial sector (as robo-advisors)\cite{Littman2021},
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} (which can also create pictures through scalable vector graphics (SVG) and code)
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
making video games\cite{Guzdial2016}.
%
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is a umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous) versus classification (discrete). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
%
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression, support vector regression.
There are also lesser know algorithms like 
evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
%
One advantage of evolutionary algorithms is that they start with a small data set
and periodically request new data in order to solve the problem iteratively.
\td{This is exactly what I needed because every experiment is very time intensive.}

@@

\Gls{pso} also uses a starting population of particles of size $p$ where each experiment 
is represented by its independent and dependent variables. 
It was originally inspired by the behaviour of bird flocks and fish school.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Particle Swarm Optimization}

it has been shown that \gls{pso} works well on problems wher \gls{ga}s work well\cite{Kennedy1995}. 
It can be seen as in the middle of \gls{ga} (taking eons) and \gls{nn} taking seconds regarding time scale\cite{Kennedy1995}.
it is a stochastic process
are there iterative optimisation processes without stochastic? 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
Contstraints might include range constraints of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}

In two cases a deliberate design of experiment makes sense. 
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}\\
\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}

>>>>

But fear not, that doesn't mean that computers are sentient or more intelligent than humans\cite{searle1980,searle1999married} and certainly not that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
%Now, we can't - it's hard to - imagine to live without electricity. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017,Feng1999,Campbell2002}, 
image recognition (very popular for medical diagnosis)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition (to prevent theft of toilet paper \cite{Andrews2017}),
financial sector (as robo-advisors)\cite{Littman2021},
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021} 
(which can also create code and pictures through scalable vector graphics (SVG))
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create graphic artwork (DALL-E 2)\cite{Marcus2022} or 
making video games\cite{Guzdial2016}.
%
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice.
Such that, after some time of general use it is no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is a umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
%
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression, support vector regression.
There are also lesser know algorithms like 
evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
%
One advantage of evolutionary algorithms is that they start with a small data set
and periodically request new data in order to solve the problem iteratively.
\td{This is exactly what I needed because every experiment is very time intensive.}

@@

\Gls{pso} also uses a starting population of particles where each experiment (particle) 
is represented by its independent and dependent variables. 
It was originally inspired by the behaviour of bird flocks and fish schools.
Each particle has an associated position and velocity. 
Every movement across the search space is stochastic and influenced by its particle velocity and position as well as its and the swarm's best known position.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Design of Experiment} %DOE
%\epigraph{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}{Grahem C. Goodwin\cite{goodwin1977experiment}}
%
\begin{quote}
	{"The real purpose of experiment design is to maximize the information content of the data within the limits imposed by the given constraints."}
	- {Grahem C. Goodwin\cite{goodwin1977experiment}}
\end{quote}
%
In two cases a deliberate design of experiment is beneficial.
If the query of a new data point is very expensive, it is favourable to actively chose the query (e.g. drilling for oil or quantum chemical calculations). 
If the query space is so vast, that randomly querying might lead to information about uninteresting part of the domain.
% 
At the beginning of an experiment its constraints must be determined. 
%
Constraints for a given experiment might include range of input and output variables as well as total time available and total number of samples/experiments that can be taken.\cite{goodwin1977experiment}
%

A naive approach to an experiment design is the full factorial \gls{doe}.
Each possible combination of discrete values is tested. 
While this is the best design it will more often than not be infeasible due the curse of dimensionality.
The 2-level factorial design provides an alternative with $2^d$ (where d is the dimensionality of the problem) experiments. 
Drawbacks of 2-level factorial include no data about the inside of the search space and infeasibility for moderate dimensional problems.

The Plackett-Burman\cite{vanaja2007design,miller2001using,wang1995hidden} design is a special case of the two level fractional factorial design, 
where the number of needed experiments is smaller than $d+2$ and 
each combination of levels for any pair of factors appears the same number of times. 
In order to overcome these obstacles a certain number of experiments can be chosen randomly from the search space. 
%A straight forward design can be to randomly chose a certain number of experiments from the search space. 
A drawback of randomization is that sample set is likely not evenly distributed across the search space\cite{viana2016tutorial}. 
The Hammersley design\cite{viana2016tutorial,diwekar1997efficient} is based on the Hammersley sequence and produces space filling data points. 
The Latin hypercube \gls{doe}\cite{viana2016tutorial,diwekar1997efficient} is a type of orthogonal \gls{doe}, 
which has the advantage that 
each level for each variable will be tested only once. 
A Latin hypercube \gls{doe} can be also created such that data points more uniformly distribute over the search space. 
%"Our ability to design a good experiment should depend upon our prior knowledge regarding the nature of the data generating mechanism."\cite{goodwin1977experiment}
%
%Continuous state spaces must be accommodated by arbitrary discretization.
\cite{cohn1996neural}
%
At

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal} very math intensive  \\
\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}  \\
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}

### 2022-08-24 Thesis/chapter/06-results-and-discussion.tex
DOE und PSO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I and PSO//Optimization}
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}
\td{too much data as input, dimensionality reduction (PCA) and optimization}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I and PSO//Optimization}
\td{ideal objective is to create response surface approximation}\\
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
The primary goal of a screening experiment is to identify the active factors. 
A secondary goal is to provide a simple model that captures the essential features of the 
relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}

@@

\subsection{DOE}
factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
